---
title: "simpleRegress"
author: "put your name here"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 
```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
ourweight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(ourweight)
summary.lm(ourweight)
```

So far the order is that our neck is better than our weight

```{r}
ourchest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(ourchest)
summary.lm(ourchest)
```

The order for worst to best would be weight, neck, and chest

```{r}
ourheadwth <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(ourheadwth)
summary.lm(ourheadwth)
```

The order for worst to best would be headwth, weight, neck, and chest

```{r}
ourheadlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(ourheadlen)
summary.lm(ourheadlen)
```

The order for worst to best would be headwth, weight, neck, chest, and headlen

```{r}
ourage <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(ourage)
summary.lm(ourage)
```
The order for worst to best would be age, headwth, weight, neck, chest, and headlen last. 

